---
title: "R Notebook"
output: html_notebook
---

```{r}
NIH_awards <- import("NIH_data.csv")
str(NIH_awards)
```

```{r}
NIH_awards %>%
  group_by(Administering_IC) %>%
  summarise(freq = n(), avg_cost = mean(Total_Cost, na.rm = TRUE)) %>%
  arrange(desc(avg_cost))
```
```{r}
get_summary_df <- function(year) {
  if (is.numeric(year)) {
    Funding_By_IC <- NIH_awards %>%
      filter(Fiscal_Year == year) %>%
      group_by(Administering_IC) %>%
      summarise(freq = n(), avg_cost = mean(Total_Cost, na.rm = TRUE)) %>%
      arrange(desc(avg_cost))
  } 
  else {
    Funding_By_IC <- NIH_awards %>%
      group_by(Administering_IC) %>%
      summarise(freq = n(), avg_cost = mean(Total_Cost, na.rm = TRUE)) %>%
      arrange(desc(avg_cost))
  }
  
  Funding_By_IC
}
```

```{r}
get_summary_df(2020)
```
# Loading in Population Mean Data, for 2019 and 2020 Specifically
```{r}
NIH_avgs_2019 <- import("NIH_Avg_Funding_19.csv")
# str(NIH_avgs_2019)

NIH_avgs_2020 <- import("NIH_Avg_Funding_20.csv")
# str(NIH_avgs_2020)
```

# Abstract Function to Run One-Sample T Test for Means
```{r}
one_sample_t_test <- function(IC_name, year, pop_data) {
  NIH_filtered <- NIH_awards %>%
    filter(Fiscal_Year == year, Administering_IC == IC_name)
  
  pop_mean <- pop_data %>%
    filter(IC == IC_name)
  
  t.test(NIH_filtered$Total_Cost, mu = (pop_mean$FUNDING_INT) / (pop_mean$AWARDS), alternative = "greater")
}
```

#------------------------------------------------------------------------------#
#---------------------HYPOTHESIS TESTS CONDUCTED BELOW-------------------------#
#------------------------------------------------------------------------------#

# Analyzing 2019: Top 5 IC's that Have Most Awarded Projects Over Time
```{r}
one_sample_t_test("NCI", 2019, NIH_avgs_2019) #sig
one_sample_t_test("NIAID", 2019, NIH_avgs_2019) #sig
one_sample_t_test("NIGMS", 2019, NIH_avgs_2019) #sig
one_sample_t_test("NHLBI", 2019, NIH_avgs_2019) #not sig
one_sample_t_test("NINDS", 2019, NIH_avgs_2019) #not sig
```

# Analyzing 2019: Top 4 IC's that Have the Largest Average Award Funding Over Time
```{r}
one_sample_t_test("NCATS", 2019, NIH_avgs_2019) #sig
one_sample_t_test("NICHD", 2019, NIH_avgs_2019) #sig
one_sample_t_test("NIAID", 2019, NIH_avgs_2019) #sig
one_sample_t_test("NHGRI", 2019, NIH_avgs_2019) #not sig
```



# Analyzing 2020: Top 5 IC's that Have Most Awarded Projects Over Time
```{r}
one_sample_t_test("NCI", 2020, NIH_avgs_2020) #not sig
one_sample_t_test("NIAID", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NIGMS", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NHLBI", 2020, NIH_avgs_2020) #not sig
one_sample_t_test("NINDS", 2020, NIH_avgs_2020) #not sig
```

# Analyzing 2020: Top 4 IC's that Have the Largest Average Award Funding Over Time
```{r}
one_sample_t_test("NCATS", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NICHD", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NIAID", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NHGRI", 2020, NIH_avgs_2020) #not sig
```



# Analyzing 2020: Top 5 IC's that Have Most Awarded Projects in 2020
```{r}
one_sample_t_test("NCI", 2020, NIH_avgs_2020) #not sig
one_sample_t_test("NIAID", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NIGMS", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NINDS", 2020, NIH_avgs_2020) #not sig
one_sample_t_test("NIA", 2020, NIH_avgs_2020) #not sig
```

# Analyzing 2020: Top 4 IC's that Have the Largest Average Award Funding in 2020
```{r}
one_sample_t_test("NCATS", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NICHD", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NIAID", 2020, NIH_avgs_2020) #sig
one_sample_t_test("NCCIH", 2020, NIH_avgs_2020) #not sig
```