---
title: "R Notebook"
output: html_notebook
---

# Necessary packages
```{r, include = FALSE}
library(rio)
library(dplyr)
library(tidyverse)
library(descr)
library(ggplot2)
library(ggthemes)
```

# Loading in Dataset
```{r}
NSF_awards <- import("Awards_IntFunding.csv")
View(NSF_awards)
```

```{r}
# glimpse(NSF_awards)
# summary(NSF_awards)
# summary(NSF_awards$Year)
```

```{r}
total_funding <- sum(NSF_awards$AwardedAmountToDate, na.rm = TRUE)

Funding_By_D_Y <- NSF_awards %>%
  filter(!is.na(AwardedAmountToDate)) %>%
  group_by(Year) %>% 
  summarise(freq = n(), avg = mean(AwardedAmountToDate) / 1000000, 
            total = sum(AwardedAmountToDate, na.rm = TRUE))

Funding_By_D_Y
#             prop_total = total / total_funding
```


# Creating dataframe grouped by directorate, and summary stats for each
```{r}
total_funding <- sum(NSF_awards$AwardedAmountToDate, na.rm = TRUE)

Funding_By_D <- NSF_awards %>%
  filter(!is.na(AwardedAmountToDate)) %>%
  group_by(NSFDirectorate) %>% 
  summarise(freq = n(), avg = mean(AwardedAmountToDate) / 1000000, 
            total = sum(AwardedAmountToDate, na.rm = TRUE),
            prop_total = total / total_funding)

Funding_By_D
```

# Plot of means (average funding for each directorate)
```{r}
Funding_By_D %>%
  ggplot(mapping = aes(x = NSFDirectorate, y = avg)) +
  geom_point(color = "blue") +
  labs(title = "Overall Average Funding For Each NSF Directorate",
       subtitle = "Education and Human Resources disproportionately receives most funding
on average, valued at $2.17M",
       x = "NSF Directorates", y = "Average Government Funding (Millions of $)",
       caption = "National Science Foundation") +
#facet_wrap(~term == c(1960, 1990)) - select particular terms to analyze
  theme_clean()
```
# Plot of proportions (allocation of total government funding to each directorate)
```{r}
Dir_Funding_Props <- data.frame(
  group = Funding_By_D$NSFDirectorate,
  value = Funding_By_D$total)

Dir_Funding_Props

ggplot(data = Dir_Funding_Props, mapping = aes(x="", y = value, 
                                                       fill = group)) +
  geom_bar(stat="identity", width = 1) +
  coord_polar("y", start=0) +
  labs(title = "Overall Allocation of Government Funding to Each Directorate",
       subtitle = "Mathematical and Physical Sciences receives greatest
proportion of government funding with 32% of the funding, followed
by Education and Human Resources") +
  theme_void()
```
```{r}
get_org_data <- function(directorate) {
  total_funding <- sum(NSF_awards$AwardedAmountToDate[NSF_awards$NSFDirectorate == directorate], na.rm = TRUE)
  Funding_by_O <- NSF_awards %>%
    filter(!is.na(AwardedAmountToDate), NSFDirectorate == directorate) %>%
    group_by(NSFOrganization) %>%
    summarise(freq = n(), avg = mean(AwardedAmountToDate / 1000000),
              total = sum(AwardedAmountToDate, na.rm = TRUE),
              prop_total = total / total_funding)
  Funding_by_O
}
```

```{r}
get_org_point_means <- function(Funding_by_O, directorate, subt) {
  Funding_by_O %>%
  ggplot(mapping = aes(x = NSFOrganization, y = avg, fill = NSFOrganization)) +
  stat_summary(fun = "mean", geom = "bar") +
  labs(title = paste0(directorate, ": Average Funding For Each NSF Organization"),
       subtitle = subt,
       x = "NSF Organizations", y = "Average Government Funding (Millions of $)",
       caption = "National Science Foundation") +
  theme_clean()
}
```

```{r}
get_org_pie <- function(Funding_by_O, directorate, subt) {
  Org_Funding_Props <- data.frame(
  Organization = Funding_by_O$NSFOrganization,
  value = Funding_by_O$total)

Org_Funding_Props

ggplot(data = Org_Funding_Props, mapping = aes(x="", y = value, 
                                                       fill = Organization)) +
  geom_bar(stat="identity", width = 1) +
  coord_polar("y", start=0) +
  labs(title = paste0(directorate, ": Overall Allocation of Government Funding to Each Organization"),
       subtitle = subt) +
  theme_void()
}
```

# Generates dataframes for each directorate
```{r}
for (i in Funding_By_D$NSFDirectorate) {
  print(get_org_data(i))
}
```
# Generates plot of means for each directorate
```{r}
subt_vec_point_means <- c("Empty sub", 
                          "Division of Molecular and Cellular Biosciences with most average funding of $0.47M", 
                          "Office of Advanced Cyberinfrastructure with most average funding of $0.38M", 
                          "Division of Research on Learning in Formal and Informal Settings 
with most average funding of $0.71M", 
                          "Division of Civil, Mechanical & Manufacturing Innovation
with most average funding of $3.75M", 
                          "Division of Ocean Sciences with most average funding of $0.41M",
                          "Division of Materials Research with most average funding of $0.83M", 
                          "Office of Integrative Activities with disproportionately
most average funding of $0.87M", 
                          "Division of Behavioral and Cognitive Sciences with most average funding of $0.32M")
subt_index <- 1
for (i in Funding_By_D$NSFDirectorate) {
  print(get_org_point_means(get_org_data(i), 
                    i, subt_vec_point_means[subt_index]) + theme(legend.position = "none"))
  subt_index <- subt_index + 1
}
subt_index <- 1
```
# Generates pie charts for each directorate
```{r}
subt_vec_pie <- c("Empty sub", 
                  "43% of funding goes towards the Division of Environmental Biology", 
                  "37% of funding goes towards Information and Intelligent Systems", 
                  "64% of funding goes towards the Division of Graduate Education", 
                  "41% of funding goes towards the Division of Engineering Education & Centers", 
                  "41% of funding goes towards the Division of Atmospheric and Geospace Sciences",
                  "35% of funding goes towards the Division of Materials Research", 
                  "73% of funding goes towards the Office of Integrative Activities", 
                  "53% of funding goes towards the Division of Social and Economic Sciences")
subt_index <- 1
for (i in Funding_By_D$NSFDirectorate) {
  print(get_org_pie(get_org_data(i), 
                    i, subt_vec_pie[subt_index]))
  subt_index <- subt_index + 1
}
subt_index <- 1
```

# Hypothesis Testing
```{r}
NSF_median_awards <- import("NSF_Median_Awards.csv")
View(NSF_median_awards)
str(NSF_median_awards)
```


```{r}
NSF_H_med_awards_2019 <- NSF_awards %>%
  filter(Year == 2019) %>%
  group_by(NSFDirectorate) %>%
  summarise(freq = n(), median_award = median(AwardedAmountToDate, na.rm = TRUE))

NSF_H_med_awards_2020 <- NSF_awards %>%
  filter(Year == 2020) %>%
  group_by(NSFDirectorate) %>%
  summarise(freq = n(), median_award = median(AwardedAmountToDate, na.rm = TRUE))

NSF_H_med_awards_2019
NSF_H_med_awards_2020
```
#------------------------------------------------------------------------------#
#---------------------HYPOTHESIS TESTS CONDUCTED BELOW-------------------------#
#------------------------------------------------------------------------------#

```{r}
one_sample_median_test <- function(directorate, year, pop_mean) {
  NSF_filtered <- NSF_awards %>%
    filter(Year == year, NSFDirectorate == directorate)
  
  median(NSF_filtered$AwardedAmountToDate, na.rm = TRUE)
  wilcox.test(NSF_filtered$AwardedAmountToDate, mu = pop_mean, alternative = "greater")
}
```


```{r}
# harvard_medians_2019 <- c(174102, 159679, 199613, 123580, 146771, 114467, 337650, 80016)
# ind <- 1
# for (dir in Funding_By_D$NSFDirectorate) {
#   print(one_sample_median_test(dir, 2019, harvard_medians_2019[ind]))
#   ind <- ind + 1
# }
# ind <- 1
                                            # Significant at alpha = 0.05?
one_sample_median_test("BIO", 2019, 174102) # 2 sided: no, 1 sided (greater): no 
one_sample_median_test("CSE", 2019, 159679) # 2 sided: yes, 1 sided (greater): yes
one_sample_median_test("EHR", 2019, 199613) # 2 sided: no, 1 sided (greater): no
one_sample_median_test("ENG", 2019, 123580) # 2 sided: no, 1 sided (greater): no
one_sample_median_test("GEO", 2019, 146771) # 2 sided: yes, 1 sided (greater): yes
one_sample_median_test("MPS", 2019, 114467) # 2 sided: yes, 1 sided (greater): yes
one_sample_median_test("O/D", 2019, 337650) # 2 sided: ??, 1 sided (greater): ??
one_sample_median_test("SBE", 2019, 80016) # 2 sided: no, 1 sided (greater): yes
```

```{r}
                                            # Significant at alpha = 0.05?
one_sample_median_test("BIO", 2020, 170518) # 2 sided: no, 1 sided (greater): no  
one_sample_median_test("CSE", 2020, 150206) # 2 sided: no, 1 sided (greater): no
one_sample_median_test("EHR", 2020, 166819) # 2 sided: no, 1 sided (greater): no
one_sample_median_test("ENG", 2020, 149007) # 2 sided: yes, 1 sided (greater): yes
one_sample_median_test("GEO", 2020, 152479) # 2 sided: no, 1 sided (greater): no
one_sample_median_test("MPS", 2020, 121541) # 2 sided: yes, 1 sided (greater): yes
# one_sample_median_test("O/D", 2020, 130499) # 2 sided: ??, 1 sided (greater): ??
one_sample_median_test("SBE", 2020, 99192) # 2 sided: no, 1 sided (greater): no

```
